Implicit yaddayadda

### 2011-10-27 papers/PLDI2012/implicitization.tex
typo

\usepackage{hyperref}

@@

@@

For the computation of disjunctive invariants, we experimented with a heuristic
of dynamic construction of the $\sigma$ function, adapted from
\cite{DBLP:conf/pldi/GulwaniZ10}.  We start with one sigle
disjunct per control point ($m=1$), and we start with an empty map $\sigma$. We also
define a maximal bound on the number of disjunct per control point, noted $M$.
$\sigma(j,k)$ is then constructed on the fly only when needed.
When $\sigma(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_k$ by the path indexed by $j$, and try to find an existing
disjunct of index $k'$ so that the convex hull of the two abstract values is
exactly the union of them. If such an index exists, then $\sigma(j,k) = k'$.
Otherwise:
\begin{itemize}
	\item if $m < M$, we increase $m$ by $1$ and define $\sigma(j,k) = m$
	\item if $m = M$, we define $\sigma(j,k) = M$
\end{itemize}

@@

\bibliographystyle{dmabbrvnat}
\bibliography{implicitization}
\end{document}

>>>>

\usepackage[pdfusetitle]{hyperref}

@@

\MM{À changer si on décide de ne plus distinguer $X^s$ et $X^d$}

To prevent the algorithm from adding too many path at a time, we
use another abstract value associated to a control point $p_j$, noted
$X_j^d$, which is distinct from $X_j^s$, and initialized to $X_j^s$.
This value is updated when a point $p_j$ is the target of a new path,
so that further SMT queries do not compute other paths with the same
source and destination if it is not needed (because these new paths
would not make $X_j^d$ grow, hence would not be returned by the SMT
solver).

@@

For the computation of disjunctive invariants, we experimented with a heuristic
of dynamic construction of the $\sigma$ function, adapted from
\cite{DBLP:conf/pldi/GulwaniZ10}.  We start with one single
disjunct per control point ($m=1$), and we start with an empty map $\sigma$. We also
define a maximal bound on the number of disjunct per control point, noted $M$.
$\sigma(j,k)$ is then constructed on the fly only when needed.
When $\sigma(j,k)$ needs to be computed, we first compute the image of the
abstract value $X_k$ by the path indexed by $j$, and try to find an existing
disjunct of index $k'$ so that the convex hull of the two abstract values is
exactly the union of them. If such an index exists, then $\sigma(j,k) = k'$.
Otherwise:
\begin{itemize}
	\item if $m < M$, we increase $m$ by $1$ and define $\sigma(j,k) = m$
	\item if $m = M$, we define $\sigma(j,k) = M$
\end{itemize}

@@

\phantomsection\addcontentsline{toc}{section}{References} 
\bibliographystyle{dmabbrvnat}
\bibliography{implicitization}
\end{document}
